### 2021-02-23 main.tex
Remove leftover content from new Conclusion by MS

An analysis of the trained recommender could reveal new insights into how the symbol precedence influences the proof search,
and how a symbol precedence should be chosen in the context of a problem so that it is likely to lead to an efficient proof search.
This might lead to a design of a new precedence heuristic
that focuses relies on aspects of input problems
that have been overlooked so far in the context of generating symbol precedences.

While using the \gls{kbo} as our simplification ordering scheme of choice,
we restricted ourselves to generating the symbol precedences,
leaving the symbol weights fixed to the constant 1 (the default behavior of \Vampire{}).
Learning to recommend the symbol weights in addition to the symbol precedences would be interesting.
\todo{FB: Be more fancy in wording.}

Training both the predicate and the function precedence using a single \gls{gcn} would yield a recommender
that only needs one pass through a \gls{gcn} to generate both predicate and function precedences for a problem.
Moreover, the model would have the possibility to exploit the properties of the function precedence
when generating the predicate precedence, and vice versa.
Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
in one training batch.
\todo{FB: Confusing?}

>>>>

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help designing new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these pattern to a human-understandable form.

\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedences
also determined by symbol \emph{weights} (we kept these fixed to the default value 1 in this work).
Learning to recommend also the symbol weights in addition to the precedences
represents an interesting avenue for future research.

The same applies to the idea of learning to recommend 
both the predicate and the function precedences using a single \gls{gcn}.
The joint learning, although more complex to design, could 
additionally discover interdependencies
between the effects of the function precedence and predicate precedence on the proof search,
while the current setup implicitly assumes that the effects are independent.
Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
in one training batch.
